

\section{SpeXtra%
  \label{spextra}%
}

\texttt{speXtra} is a tool to manage and manipulate astronomical spectra.

Documentation: \url{https://spextra.readthedocs.io/}

Code Base: \url{https://github.com/miguelverdugo/speXtra}

Continuous integration: \url{https://travis-ci.org/github/miguelverdugo/speXtra}

Author: Miguel Verdugo


\subsection{Functionality%
  \label{functionality}%
}

\texttt{speXtra} packages several \texttt{synphot} workflows in simple-to-use methods that allow the user
to manipulate astronomical spectra. It is intended to be the main spectral engine for \texttt{ScopeSim\_templates}
but its design also allows standalone use.

Using \texttt{speXtra}, the user can extract the magnitude from an astronomical spectrum or
scale the spectrum to that magnitude, the spectrum can be redshifted or
blueshifted or smoothed with a velocity kernel, add emission or absorption lines,
rebin the spectra or correct it for an extinction curve, etc. \texttt{speXtra} however does not perform
measurements, with the sole exception of extracting magnitudes within a passband.

\texttt{speXtra} also comes with a built-in database of spectral templates  that cover many possible user cases.
Loading these templates is as easy as typing \texttt{Spextrum('library\_name/template\_name')}. The user
can also read their own spectra from a file.


\subsubsection{Database%
  \label{database}%
}

The \texttt{speXtra} database contains libraries of spectral templates, extinction curves and filter systems.
The data is downloaded on-the-fly when requested and kept cached in the local hard drive for future use.

The scheme is flexible and additional data can be added.
In the following a short summary of the database contains is provided.


\subsubsection{Spectral Templates%
  \label{spectral-templates}%
}

At the time of writing the following libraries are included in the \texttt{speXtra} database.
Other can be added at request of the user.

\begin{itemize}
\item The Kinney-Calzetti Spectral Atlas of Galaxies

\item Pickles Stellar Library

\item SDSS galaxy composite spectra

\item IRTF spectral library

\item AGN templates

\item Emission line nebulae

\item Galaxy SEDs from the UV to the Mid-IR

\item Kurucz 1993 Models (subset)

\item Supernova Legacy Survey templates (subset)

\item Flux/Telluric standards with X-Shooter

\item High-Resolution Spectra of Habitable Zone Planets (example)
\end{itemize}

More templates can be easily added to the database at request of the users.


\subsubsection{Extinction Curves%
  \label{extinction-curves}%
}

Extinction curves provided with the database.

\begin{itemize}
\item Gordon LMC/SMC extinction curves

\item Cardelli MW extinction curves

\item Calzetti starburst attenuation curve
\end{itemize}

More templates can be easily added to the database at request of the users.


\subsubsection{Filter Systems%
  \label{filter-systems}%
}

\texttt{speXtra} currently relies on the spanish SVO filter database to download filters transmission curves.
This is done thanksto the \texttt{tynt} package. However this database is not complete and in particular filters for upcoming
ELT instruments are missing. For that reason we have added some filter management to \texttt{speXtra}.

Filter system currently included

\begin{itemize}
\item MICADO filter system

\item METIS filter system
\end{itemize}

More templates can be easily added to the database at request of the users.


\subsubsection{Installation%
  \label{installation}%
}

To install \texttt{speXtra} simply type:

\begin{quote}
\begin{alltt}
\begin{lstlisting}[frame=single]
pip install spextra
\end{lstlisting}
\end{alltt}
\end{quote}


\subsubsection{Dependencies%
  \label{dependencies}%
}

\texttt{speXtra} require the following dependencies to properly work. If they are missing they are automatically
installed.

\begin{itemize}
\item \texttt{numpy}

\item \texttt{scipy}

\item \texttt{astropy}

\item \texttt{synphot}

\item \texttt{PyYAML}

\item \texttt{tynt}
\end{itemize}


\subsection{Examples%
  \label{examples}%
}

Load the S0 template from the Kinney-Calzetti library and then plot it for quick examination.

\DUadmonition[system-message]{
\DUtitle[system-message]{system-message}


{\color{red}ERROR/3} in \texttt{<string>}, line~122

Unknown directive type \textquotedbl{}plot\textquotedbl{}.

\begin{quote}
\begin{alltt}
\begin{lstlisting}[frame=single]
.. plot::
   :context: reset
   :include-source:
   :align: center

    from spextra import Spextrum

    sp = Spextrum("kc96/s0")
    sp.plot()


\end{lstlisting}
\end{alltt}
\end{quote}
backrefs: }

It is possible to arithmetic operations with spectra

\DUadmonition[system-message]{
\DUtitle[system-message]{system-message}


{\color{red}ERROR/3} in \texttt{<string>}, line~135

Unknown directive type \textquotedbl{}plot\textquotedbl{}.

\begin{quote}
\begin{alltt}
\begin{lstlisting}[frame=single]
.. plot::
   :context: reset
   :include-source:
   :align: center

    from spextra import Spextrum

    sp1 = Spextrum("kc96/s0")
    sp2 = Spextrum("agn/qso")
    sp = sp1 + 0.3*sp2
    sp.plot()


\end{lstlisting}
\end{alltt}
\end{quote}
backrefs: }

Scaling the spectra to a magnitude and see what we get afterwards

\DUadmonition[system-message]{
\DUtitle[system-message]{system-message}


{\color{red}ERROR/3} in \texttt{<string>}, line~150

Unknown directive type \textquotedbl{}plot\textquotedbl{}.

\begin{quote}
\begin{alltt}
\begin{lstlisting}[frame=single]
.. plot::
    :context: reset
    :include-source:
    :align: center

    from spextra import Spextrum

    sp1 = Spextrum("kc96/s0")
    sp2 = sp1.scale_to_magnitude(amplitude=13 * u.ABmag, filter_name="g")

    print(sp2.get_magnitude(filter_name="g")


\end{lstlisting}
\end{alltt}
\end{quote}
backrefs: }

Adding emission lines

\DUadmonition[system-message]{
\DUtitle[system-message]{system-message}


{\color{red}ERROR/3} in \texttt{<string>}, line~165

Unknown directive type \textquotedbl{}plot\textquotedbl{}.

\begin{quote}
\begin{alltt}
\begin{lstlisting}[frame=single]
.. plot::
    :context: reset
    :include-source:
    :align: center

    from spextra import Spextrum
    import astropy.units as u

    sp1 = Spextrum("kc96/s0")
    sp2 = sp1.add_emi_lines(center=4000, flux=4e-13, fwhm=5*u.AA)

    sp2.plot()

\end{lstlisting}
\end{alltt}
\end{quote}
backrefs: }
