

\section{Essentials: Documentation and Downloads%
  \label{essentials-documentation-and-downloads}%
}


\subsection{Online Documentation%
  \label{online-documentation}%
}

Online documentation for the main packages in the ScopeSim environment can be found here:

\begin{itemize}
\item ScopeSim: \url{https://scopesim.readthedocs.io/en/latest/}

\item ScopeSim\_Templates: \url{https://scopesim-templates.readthedocs.io/en/latest/}

\item IRDB: \url{https://github.com/astronomyk/irdb}
\end{itemize}

The original SimCADO package is described here:

\begin{itemize}
\item SimCADO: \url{https://simcado.readthedocs.io/en/latest/}
\end{itemize}

\DUadmonition[note]{
\DUtitle[note]{Note}

In the near future we will release a wrapper for the ScopeSim engine and the MICADO instrument package.

The doumentation for this will be added to the original \href{https://simcado.readthedocs.io/en/latest/}{SimCADO} read-the-docs page
}


\subsection{Downloading ScopeSim and the MICADO packages%
  \label{downloading-scopesim-and-the-micado-packages}%
}

The ScopeSim engine is installed using pip:

\begin{quote}
\begin{alltt}
\begin{lstlisting}[frame=single]
$ pip install scopesim
\end{lstlisting}
\end{alltt}
\end{quote}

The casual user will also probably want to install the templates package, which contains helper functions for generating descriptions of on-sky targets like elliptical galaxies or star clusters:

\begin{quote}
\begin{alltt}
\begin{lstlisting}[frame=single]
$ pip install scopesim_templates
\end{lstlisting}
\end{alltt}
\end{quote}

Once ScopeSim is available to the local Python (version >= 3.5) installation, the user must download \textbf{ALL} the required instrument packages from the server:

\begin{quote}
\begin{alltt}
\begin{lstlisting}[frame=single]
from scopesim.server import download_package
download_package(["locations/Armazones",
                  "telescopes/ELT",
                  "instruments/MAORY",
                  "instruments/MICADO",
                  "instruments/MICADO_Sci"])
\end{lstlisting}
\end{alltt}
\end{quote}

\DUadmonition[note]{
\DUtitle[note]{Note}

There are two (2) MICADO packages available: \texttt{MICADO} and \texttt{MICADO\_Sci}.
}

For those interested in quick results, \texttt{MICADO\_Sci} provides a reduced version of the MICADO package that contains all the major effects expected from the MICADO optical system.
For those more concerned with accuracy, the standard \texttt{MICADO} package contains all expected optical effects.
\texttt{MICADO} was originally developed for the development of the reduction pipeline, and therefore contains many effects that are beyond the scope of normal science case feasability studies.


\subsection{A quick note on Primary vs Support packages%
  \label{a-quick-note-on-primary-vs-support-packages}%
}

Each package contains descriptions of the optical effects associated with an optical element.
For example the ELT package contains only the radiometric curves (e.g. transmission, emissivity, reflection) associated with the five ELT mirrors.

Packages are split into two categories: Primary and Support packages.

\textbf{Primary packages} contain detector modules that enable an on-sky target to be observed.
Without a (single) primary package, ScopeSim will not be able to produce any simulated data.
Examples of primary packages are: MICADO, METIS, HAWKI, NACO, etc

\textbf{Support packages} do not contain detector modules.
They're main function is to add the additional optical effects associated with the common optical components of an optical system.
\texttt{Armazones}, \texttt{ELT}, and \texttt{MAORY} are examples of such support packages.

Just like in real life, observing with only MICADO would be a difficult task.
Therefore we highly encourage the user to also download the support packages needed by MICADO.
